\begin{reviewer}
The author  replies to the previously proposed questions are satisfactory in general.
\end{reviewer}
\begin{authors}
Thank you.
\end{authors}

\begin{reviewer}
\clabel{5}{1}
However, the reviewr still has the concerns with the answers to the speedup and related equation (3) in the paper.

Foundamentally, the author used different method to solve the thermal equations. For the MC, the author use the traditional stable appraoch such as Runge-Kutta method, which allows any time step used. While  in the proposed statisitcal method using PC, it used the explicit iterative method as shown in (3). This explicit Forward Euler intergattion method will of course be much much faster than the Runge-Kutta method as it will not need to solve (performing LU decompostion) the matrix at all.  But this explicit integration method will only converge for very small time steps (the time step allowed actually depends on the finite difference discretization steps).

Since the explicit iteration formulat (3) is important for the proposed method to consider power and temperature interplay, the proposed method thus has severe limitations due to the time step restirctions.  The author should be provide more explanation on this issue.
\end{reviewer}
\begin{authors}
It is indeed an important concern, and we would like to respond with a detailed answer.
We assume that the reviewer is referring to the standard explicit/forward Euler method.
The reviewer is absolutely right that this method has poor stability properties; however, we do not use Euler's method in our work.
As shown in App.~A, the thermal system is solved using an exponential integrator method [Hochbruck, 2010],\footnote{This reference has been added in the revised manuscript.} which we shall demonstrate shortly.

Let us first digress from numerical integration schemes and investigate some aspects of our problem.
Combining Eq.~(1) and Eq.~(2) and dropping the details that are irrelevant for the present discussion, the system of ordinary differential equations under consideration is
\begin{equation}
  \frac{d\vX(\t)}{d\t} = \mA \: \vX(\t) + \mB \: \vP(\t, \vX(\t)) \tag{$\ast$}
\end{equation}
where $\vP$ is a nonlinear function of $\vX$.
A detailed description of the thermal system can be found in App.~A (see also [Ukhov, 2012]); for our purposes, it is sufficient to recall that
\[
  \mA = -\mC^{-\frac{1}{2}} \mG \mC^{-\frac{1}{2}}
\]
where $\mC$ and $\mG$ are the thermal capacitance and conductance matrices, respectively.
By the construction of thermal RC circuits imposed by the nature of the modeled phenomenon [Skadron, 2004], both matrices are real, symmetric, and positive definite,\footnote{It is also explained in the source code of HotSpot (v5.02), namely, in \texttt{temperature\char`_block.c}, lines 278--289, which can be downloaded at \url{http://lava.cs.virginia.edu/HotSpot/}.} and $\mC$ is also diagonal.
It follows that $\mA$ is also real and symmetric as
\[
  \mA^T = (-\mC^{-\frac{1}{2}} \: \mG \: \mC^{-\frac{1}{2}})^T = -(\mC^{-\frac{1}{2}})^T \: \mG^T \: (\mC^{-\frac{1}{2}})^T = \mA.
\]
Since $\mG$ and $\mA$ are real and symmetric, both admit the eigenvalue decomposition [Press, 2007], and the corresponding eigenvectors are orthogonal.
Let this decomposition for $\mA$ be
\[
    \mA = \m{U} \m{\Lambda} \m{U}^T
\]
where $\m{U}$ and $\m{\Lambda}$ are a matrix of the eigenvectors and a diagonal matrix of the eigenvalues $\lambda_i$ of $\mA$, respectively; a similar representation can be obtained for $\mG$.
Since $\mG$ is positive definite, all its eigenvalues are positive by definition.
Due to the relation between $\mG$ and $\mA$ given earlier, the matrices share the same eigenvalues, but they are of opposite signs.
Therefore,
\[
  \lambda_i < 0, \qquad \forall i,
\]
meaning that $\mA$ is a negative-definite matrix.

Now, denote by $\m{J}(\t, \vX(\t))$ the Jacobian matrix of $\vP(\t, \vX(\t))$ with respect to $\vX(\t)$.
It can be shown [Olver, 2006]\footnote{P. Olver and C. Shakiban. \emph{Applied Linear Algebra}. Pearson Prentice Hall, 2006. This book is not cited in the manuscript. Extra chapters of this book---which are also relevant to the present discussion, in particular, Chapters 19 and 20---are available online at \url{http://www.math.umn.edu/~olver/appl.html}.} that the system in Eq.~($\ast$) is asymptotically stable if
\[
  \zeta_i < 0, \qquad \forall i,
\]
where $\zeta_i$ are the eigenvalues of
\begin{equation}
  \mA + \mB \: \m{J}(\t, \vX(\t)). \tag{$\ast\ast$}
\end{equation}
Since the considered problem is assumed to be well posed [Gustafsson, 2008],\footnote{B. Gustafsson. \emph{High Order Difference Methods for Time Dependent PDE}. Springer Series in Computational Mathematics, 2008. This book not cited in the manuscript.} this condition should hold.
In other words, the perturbation of the eigenvalues $\lambda_i$ of $\mA$---which are all negative as it was shown earlier---caused by the derivative of the nonlinear term results in negative eigenvalues $\zeta_i$.

Let us return to numerical solutions of Eq.~($\ast$).
If the explicit Euler method was utilized, the iterative procedure would be as follows:\footnote{For the clarity of our answer, we shall use a different indexing of the power term than the one used in the manuscript, which has no effect on the generality of the corresponding conclusions.}
\begin{align*}
  \vX_k & = \vX_{k - 1} + \Delta \t \: (\mA \: \vX_{k - 1} + \mB \: \vP_{k - 1}) \\
  & = (\mI + \Delta \t \: \mA) \vX_{k - 1} + \Delta \t \: \mB \: \vP_{k - 1} \\
  & = \hat{\mCF} \vX_{k - 1} + \hat{\mCS} \vP_{k - 1}
\end{align*}
where $\vX_k = \vX(\t_k)$, $\vP_k = \vP(\t_k, \vX(\t_k))$, and $\Delta \t$ is the time step of integration.
It can be shown that $\Delta \t$ needed for the above iterative procedure to be asymptotically stable is dictated by the matrix in Eq.~($\ast\ast$).
More precisely, the following inequality should be satisfied for each eigenvalue $\zeta_i$ of that matrix:
\[
  |1 + \Delta \t \: \zeta_i | < 1.
\]
As it can be seen, and as it was mentioned by the reviewer, there is a strict limitation on $\Delta \t$ due to the narrow stability region inherent to the explicit Euler method:
\[
  \Delta \t < \frac{2}{\max_i |\zeta_i|}.
\]

In our work, we do not use the integration method described above.
Instead, we proceed as follows [Ukhov, 2012].
Multiplying both sides of Eq.~($\ast$) by $e^{- \mA \t}$ and noting that
\[
  e^{-\mA \t} \frac{d\vX(\t)}{d\t} = \frac{d\, e^{-\mA \t} \vX(\t)}{d\t} + \mA e^{-\mA \t} \vX(\t) = \frac{d\, e^{-\mA \t} \vX(\t)}{d\t} + e^{-\mA \t} \mA \vX(\t),
\]
we obtain the exact solution of Eq.~($\ast$) over a time interval $\Delta \t = \t_k - \t_{k - 1}$:
\[
  \vX(\t_k) = e^{\mA \Delta \t} \vX(\t_{k - 1}) + \int_0^{\Delta \t} e^{\mA (\Delta t - \tau)} \mB \: \vP(\t_k + \tau, \vX(\t_k + \tau)) \: d\tau.
\]
Next, the integral on the right-hand side is approximated by assuming that, within $\Delta \t$, the power dissipation does not change and is equal to the power dissipation at $\t_k$, which we write in App.~A.
Then, the approximated solution is
\[
  \vX(\t_k) = e^{\mA \Delta \t} \vX(\t_{k - 1}) + \mA^{-1}(e^{\mA \Delta \t} - \mI) \mB \: \vP(\t_{k - 1}, \vX(\t_{k - 1})),
\]
which leads to our recurrence
\[
  \vX_k = \mCF \: \vX_{k - 1} + \mCS \: \vP_{k - 1}
\]
where
\[
  \mCF = e^{\mA \Delta t} \hspace{1em} \text{and} \hspace{1em} \mCS = \mA^{-1} (e^{\mA \Delta \t} - \mI) \: \mB.
\]
Since $\mA$ is real and symmetric, which was shown earlier, the matrix exponential and matrix inverse needed for the recurrence are efficiently computed as described in [Ukhov, 2012].

The solution technique that we use in the proposed framework belongs to the family of exponential integrators [Hochbruck, 2010].
This particular member of that family is a one-step method based on the function value from the previous iteration.
This makes the method appear similar to the explicit Euler method, which was also noted by the reviewer.\footnote{Due to this similarity, the method is sometimes referred to as the exponential Euler method; in order to avoid any confusion, we do use this terminology here.}
However, the stability properties of the two approaches are considerably different, which we shall discuss next.

In contrast to Euler's method, the utilized exponential integrator evaluates the linear part of the thermal system exactly, which eliminates potential issues from this side.
In order to further investigate the behaviors of the two methods, let us unfold their recurrent expressions and compare the cumulative influences of $\hat{\mCF}$ and $\mCF$:
\[
  \vX_k = \sum_{i = 1}^k \tilde{\mCF}^{k - i} \: \mCS \: \vP_{i - 1}
\]
where $\vX_0 = \mZero$ is taken into account, and $\tilde{\mCF}$ stands for either $\hat{\mCF}$ or $\mCF$.
Due to the negative-definiteness of $\mA$ discussed earlier, $\mCF = e^{\mA \Delta \t}$ is a convergent matrix [Olver, 2006] for any positive $\Delta \t$.
Therefore, under the assumption that the problem is well posed, as our iterative procedure advances, the increasing powers of $\mCF$ prevents the numerical solution from an unbounded growth [Hochbruck, 2010], which is expected from $\hat{\mCF} = \mI + \Delta \t \mA$ of Euler's method with an inadequately chosen time step.

To conclude, the time step used in the recurrence given by Eq.~(3) does not impose severe limitations on the proposed framework.

\begin{actions}
  \action{The solution method used by our framework has been clarified in App.~A.}
  \action{The corresponding reference to [Hochbruck, 2010] has been included in the bibliography.}
\end{actions}
\end{authors}

\begin{reviewer}
\clabel{5}{2}
Actually, going back the speedup issue, the review thinks that a more fair comparision is to use (3) for MC run as well (If PC based method can use it with stable results, then it should work for tranisent anlysis by MC).
\end{reviewer}
\begin{authors}
The reviewer is referring to \cref{5}{10 (Revision 1)}.
In our answer to that comment, we explained what had been done in order to achieve the reported speedups of the proposed framework.
In our answer to this new comment, we would like to recall several aspects mentioned last time and give a further elaboration on them.

Our solution does not adhere to the traditional way of constructing non-intrusive PC expansions; it can be classified as semi-intrusive, if you will.
If we took the traditional approach, our framework would be competing with the MC-based approach in terms of the number of calls to a numerical solver of the thermal system.
In such a case, the speedup would be the ratio between the number of MC samples $\nsamples$ and the number of quadrature nodes $\qdorder$ needed for non-intrusive spectral projections.
However, we have taken a different route: we perform PC expansions in a step-wise manner based on the exponential iterator method described earlier.
Consequently, the reported speedups of the proposed framework are due to two major factors: PC expansions \perse\ and the recurrence-based solution process of the thermal model.
This aspect has been emphasized in the manuscript as one of the actions taken with respect to \cref{5}{10 (Revision 1)}.

The reviewer is right that our approach for solving the thermal system could also be used for MC sampling.
In this case, we would return to the aforementioned comparison in terms of the number of solver calls.
However, we consider the chosen solution method as an part of our research.
As we replied to \cref{5}{9 (Revision 1)}---that comment was concerned with alternative MC sampling techniques such as quasi-MC sampling---MC sampling was not our focal point, and we put all our efforts into the development of the proposed framework rather than into the exploration of possibilities with the MC-based approach.

Let us also mention the following.
We did not want to compromise the assessment of the proposed framework and, therefore, tried to eliminate any additional assumptions from MC sampling; we tried to keep MC sampling pure.
There are two main aspects in this regard.
First of all, the model order reduction procedure described in App.~B is not performed inside the MC-based approach: MC sampling preserves 100\% of the variance of the problem and, thus, operates on all the random variables.
Second, the assumption about the constant power dissipation between successive moments of time described in App.~A is not made by the MC-based approach: MC sampling solves the initial problem directly and, thus, accounts for the variability of power within each $\Delta \t$.
To elaborate, MC sampling is based on the fourth- and fifth-order Runge-Kutta formulae available in MATLAB, namely, on the well-known \texttt{ode45} routine, which implements the Dormand-Prince method.
We would like to emphasize that, similar to our exponential iterator, this method is explicit and, therefore, has no need of such techniques as the LU decomposition mentioned in \cref{5}{1}.
However, \texttt{ode45} uses an advanced approximation scheme and, thus, is considered to be a reliable general-purpose solver that typically delivers accurate results; therefore, we use it as the etalon for the comparison given in Sec.~VII.

\begin{actions}
  \action{The solution method used by the MC approach has been clarified in Sec.~VII.}
  \action{It has been noted that MC sampling preserves the whole variance of the problem.}
\end{actions}
\end{authors}

\begin{reviewer}
\clabel{5}{3}
The author should give the time step used for the transient simulation using~(3).
\end{reviewer}
\begin{authors}
The time step used in the experimental results is given in the last but one paragraph of Sec.~VII, and it is equal to 1$\,\text{ms}$.
The reviewer is right that we did not mention explicitly that it was the time step of the iterative procedure in Eq.~(3); it has been fixed in the revised manuscript.

\begin{actions}
  \action{It has been clarified in Sec.~VII that the reported time step of power and temperature traces is the time step of the iterative procedure in Eq.~(3)/Eq.~(7).}
\end{actions}
\end{authors}

\begin{reviewer}
\clabel{5}{4}
In summary, if (3) is essential for the proposed method, the author should mention this limitation and its impacts on the mentioned contribuations in this paepr.
\end{reviewer}
\begin{authors}
We hope that our answers to the previous comments and the corresponding modifications of the manuscript clarify the important concerns brought up by the reviewer.
Thank you for the thorough revision of the paper.
\end{authors}
