% Similar to IEEEbiographynophoto from IEEEtran.cls
\newenvironment{biography}{\vspace{1em}\footnotesize}{\relax\par\normalfont}

\begin{biography}
\noindent\textbf{Ivan Ukhov} received the B.Sc. and M.Sc. degrees (both with honors) in computer science and computer engineering from St.~Petersburg State Polytechnical University, St.~Petersburg, Russia, in 2008 and 2010, respectively.

He is currently a Ph.D. candidate at the Department of Computer and Information Science, Link\"{o}ping University, Link\"{o}ping, Sweden.
His research is concerned with uncertainty quantification for electronic system design.
\end{biography}

\begin{biography}
\noindent\textbf{Petru Eles} (M'99) is Professor of Embedded Computer Systems with the Department of Computer and Information Science (IDA), Link\"{o}ping University.
Petru Eles' current research interests include embedded systems, real-time systems, electronic design automation, cyber-physical systems, hardware/software codesign, low power system design, fault-tolerant systems, design for test.
He has published a large number of technical papers in these areas and co-authored several books.
Petru Eles received two best paper awards at the European Design Automation Conferences (EURO-DAC), a best paper award at the Design Automation and Test in Europe Conference (DATE), and a best paper award at the International Conference on Hardware/Software Codesign and System Synthesis (CODES/ISSS).

Prof. Eles is an Associate Editor of the IEEE Transactions on Computers, the IEEE Design \& Test, and of the IET Proceedings - Computers and Digital Techniques.
\end{biography}

\begin{biography}
\noindent\textbf{Zebo Peng} (M'91--SM'02) is Professor of Computer Systems, Director of the Embedded Systems Laboratory, and Chairman of the Division for Software and Systems in the Department of Computer Science, Link\"{o}ping University.
He has published more than 300 technical papers and four books in various topics related to embedded systems, and has received four best paper awards and one best presentation award in major international conferences.
\end{biography}
