\input{include/assets/algorithm.tex}
The probability space that we shall reside in is defined as a triple $(\outcomes, \sAlgebra, \pMeasure)$ where $\outcomes$ is a set of outcomes, $\sAlgebra \subseteq 2^\outcomes$ is a $\sigma$-algebra on $\outcomes$, and $\pMeasure: \sAlgebra \to [0, 1]$ is a probability measure \cite{maitre2010}.
A random variable is a function $X: \o \in \outcomes \mapsto X(\o) \in \real$ which is $\sAlgebra$-measurable.
A random vector (matrix) is then a vector (matrix) whose elements are random variables.
In order to make a clear distinction between deterministic and stochastic quantities, the latter will be written as $X(\o)$, which should not be confused with a point evaluation.
In what follows, the probability space $(\outcomes, \sAlgebra, \pMeasure)$ is always implied.

Consider a heterogeneous electronic system that consists of $\nprocs$ processing elements and is equipped with a thermal package.
The processing elements are the active components of the system identified at the system level (ALUs, FPUs, caches, \etc).
Let $\system$ be a thermal specification of the system defined as a collection of temperature-related information: (a) the floorplans of the active layers of the chip; (b) the geometry of the thermal package; and (c) the thermal parameters of the materials that the chip and package are made of (\eg, the silicon thermal conductivity and specific heat).

A (transient) power profile $\profileP$ is defined as a tuple composed of a data matrix $\mP = (\vP_i) \in \real^{\nprocs \times \nsteps}$, $\vP_i \in \real^\nprocs$, that captures the power dissipation of the $\nprocs$ processing elements at $\nsteps$ moments of time and a (column) vector $\partition{\mP} = (\t_i) \in \real^{\nsteps}$ with positive and strictly increasing components that specifies these moments of time.
The definition of a (transient) temperature profile $\profileT$ is the same as the one for power except that the data matrix $\mTO$ contains temperature.

The system depends on a set of process parameters that are uncertain at the design stage; these parameters are denoted by a random vector $\vU(\o)$.
Once the fabrication process yields a particular outcome $\o \in \outcomes$, $\vU(\o)$ takes (potentially) different values for each fabricated chip individually and stays unchanged thereafter.
Consequently, $\vU(\o)$ leads to deviations of the actual power dissipation from nominal values and, thus, to deviations of temperature from the one corresponding to the nominal power consumption.
In what follows, we shall make a distinction between deterministic and stochastic profiles.
In the latter case, the power and temperature profiles are denoted by $\profileP{\o}$ and $\profileT{\o}$, respectively.

The goal of this work is to develop a system-level probabilistic framework for power-temperature analysis (PTA) of electronic systems where the actual power dissipation and temperature are stochastic due to their dependency on the set of uncertain parameters $\vU(\o)$.\footnote{Although the focal point of this paper is process variation, there can be other uncertainties such as those related to the system load and environment.}
The user is required to: (a) provide a thermal specification of the platform $\system$; (b) have prior knowledge (or belief) on the probability distribution of the uncertain parameters (\sref{uncertain-parameters}); and (c) specify a power model, in which $\vU(\o)$ is an input (\sref{power-model}).
The framework should provide the user with the tools to analyze the system under a given workload, without imposing any constraints on the nature/origins of this workload, and obtain the corresponding stochastic power $\profileP{\o}$ and temperature $\profileT{\o}$ profiles with a desired level of accuracy and at low costs.
