\input{include/assets/algorithm.tex}
In a nutshell, the goal stated in \sref{problem-formulation} is achieved as follows. First, we begin with the commonly found formalism of constructing a thermal model given a thermal specification $\system$. Due to the complexity of the underlying physical phenomenon---that is, the heat trasfer within a multiprocessor system---such a model is inherently expensive from the computational perspective, which makes straightforward MC-based analyses prohibited and often infiasible. Instead, we construct a surrogate model, or a meta model, which is light, \ie, the effords needed to obtain power and temperature traces given an assignment of the uncertain parameters are negligible compared to those needed for the initial problem formulation. This light model can now undergo the same MC sampling as one might think of at the very beginning, but this time the procedure is performed in a much more efficient manner; therefore, such quantities as \cdfs\ and \pdfs\ can be trivially estimated. Moreover, the constructed surrogate provides analytical formulae for the moments, \ie, the expected value, variance, \etc\ are readily available without any sampling.

The the major steps of our technique are depicted in \fref{algorithm} and are spelled out below.

\step{1}{Uncertain Parameters (\sref{uncertain-parameters}).} Polynomial chaos (PC) empoled in this paper to construct surrogate models operates on a finite set of independent \rvs. The uncertain parameters $\vU(\o)$ might not satisfy this requirement and, therefore, should be first preprocessed; the output is denoted by $\vZ(\o)$.

\step{2}{Power Model (\sref{power-model}).} The model of the power dissipation is formalized at this stage, \ie, the user defines the effect that the uncertain parameters have on the power consumption of the system. It can be a closed-form formula, a piece of code, \etc\ that takes in an assignment $\vU \equiv \vU(\o)$, for some fixed $\o$, along with the current temperature and outputs the corresponding power. It is worth being noted that the transformation is purely deterministic.

\step{3}{Thermal Model (\sref{thermal-model}).} With respect to the thermal specification $\system$ (see \sref{problem-formulation}), a mathematical representation of the thermal system is constructed. The representation closely interacts with the power model from Stage~2 and produces the corresponding power and temperature profiles for a given nominal dynamic power profile and an assignment $\vU$. As at Stage~2, the model produced at Stage~3 acts deterministically. In the context of the MC sampling, these computations are to be performed thousands of times with different assignments $\{ \vU_i \}_{i = 1}^{\mcsamples}$ of $\vU(\o)$, for some large $\mcsamples$, which, as motivated earlier, is typically prohibited in practice.

\step{4}{Surrogate Model (\sref{polynomial-chaos}).} The major part, wherein the surrogate model is atteined by traversing the given nominal power profile and gradually constructing polynomial expansions for the stochastic power and temperature profiles in terms of the processed uncertain parameters from Stage~1. The output is essentially a substitute to the problem defined at Stage~3 with respect to the power model determined at Stage~2.

\step{5}{Post-processing (\sref{output-processing}).} The computed PC expansions are analyzed in order to obtain the desired characteristics of the system, \eg, \cdfs, \pdfs, moments.

\subsection{Uncertain Parameters} \slabel{uncertain-parameters}
\input{include/proposed-framework/uncertain-parameters.tex}

\subsection{Power Model} \slabel{power-model}
\input{include/proposed-framework/power-model.tex}

\subsection{Thermal Model} \slabel{thermal-model}
\input{include/proposed-framework/thermal-model.tex}

\subsection{Surrogate Model} \slabel{polynomial-chaos}
\input{include/proposed-framework/polynomial-chaos.tex}

\subsection{Post-processing} \slabel{output-processing}
\input{include/proposed-framework/output-processing.tex}
