Given a platform description $\system$ (see \sref{architecture-model}), an equivalent thermal RC circuit with $\nodes$ \definition{thermal nodes} is constructed \cite{kreith2000}. The structure of the circuit depends on the intended level of details defining the resulting accuracy. The thermal behaviour of the circuit is modeled with the following system of differential-algebraic equations (DAEs) with the state-space dimension equal to $\nodes$:
\begin{numcases}{}
  \mC \frac{d\vTI(\t, \o)}{d\t} + \mG \vTI(\t, \o) = \mM \vP(\t, \o) \elabel{fourier-original} \\
  \vTO(\t, \o) = \mM^T \vTI(\t, \o) + \vTO_\amb \nonumber
\end{numcases}
$\mC, \mG \in \real^{\nodes \times \nodes}$ are the matrices of the thermal capacitance and conductance, respectively. $\mC$ is a diagonal matrix with positive elements, and $\mG$ is a symmetric, positive-definite matrix. $\vTI \in \real^\nodes$ is the state vector of the system, which corresponds to the difference between the temperature of the thermal nodes and the ambient temperature. $\vP \in \real^\cores$ is the input vector of the power dissipation of the processing elements (see \eref{power-model}), and $\mM \in \real^{\nodes \times \cores}$ is its mapping matrix to the thermal nodes. $\vTO \in \real^\cores$ is the output vector of the system, which is the temperature of the processing elements, and $\vTO_\amb \in \real^\cores$ is the vector of the ambient temperature, which, for clarity of presentation and without loss of generality, we model as a deterministic variable.

For convenience, we perform an auxiliary transformation \cite{ukhov2012} of the original thermal model given above. Let $\vX = \mC^\ifrac{1}{2} \vTI$, $\mA = -\mC^{-\ifrac{1}{2}} \mG \mC^{-\ifrac{1}{2}}$, and $\mB = \mC^{-\ifrac{1}{2}} \mM$, then\footnote{Since $\mC$ is diagonal, the transformation is cheap to undertake.}
\begin{subnumcases}{\elabel{fourier-system}}
  \frac{d\vX(\t, \o)}{d\t} = \mA \vX(\t, \o) + \mB \vP(\t, \o) \elabel{fourier-de} \\
  \vTO(\t, \o) = \mB^T \vX(\t, \o) + \vTO_\amb \elabel{fourier-output}
\end{subnumcases}
where $\vX$ is the new state vector. It should be noted that the coefficient matrix $\mA$ preserves the  symmetry and positive-definiteness of $\mG$. In general, \eref{fourier-de} is a \emph{nonlinear} system of differential equations due to the power term, which has a nonlinear dependency on temperature (see \eref{power-model}). Hence, there is no closed-form solution to \eref{fourier-de}.

Since the input power profile $\prof{\mP_\dyn}$ is discrete in time by definition (\sref{system-profiles}), it is natural to assume that the dynamic power stays constant between neighboor samples. (Otherwise, if power undergoes dramatical changes, one needs to capture a finer profile.) Also, since the time intervals $\{ \dt_i \}_{i = 1}^{\steps}$ are short enough, the leakage power can be safely approximated by a constant within one interval. Therefore, if we focus only on $\t \in [0, \dt]$, \eref{fourier-de} can be rewritten as
\begin{equation} \elabel{fourier-ode}
  \frac{d\vX(\t, \o)}{d\t} = \mA \vX(\t, \o) + \mB \vP(0, \o)
\end{equation}
where $\vP(0, \o)$ is the power dissipation at the beginning of the time interval (with respect to the corresponding temperature). \eref{fourier-ode} is a system of ordinary differential equations (ODEs), which can be solved analyticaly. The solution is
\begin{equation} \elabel{ode-solution}
  \vX(\t, \o) = \mE(\t) \vX(0, \o) + \mD(\t) \vP(0, \o)
\end{equation}
where $\t \in [0, \dt]$ and
\begin{align}
  & \mE(\t) = e^{\mA \t} \in \real^{\nodes \times \nodes} \elabel{e} \\
  & \mD(\t) = \mA^{-1} (e^{\mA \t} - \mI) \mB \in \real^{\nodes \times \cores} \elabel{d}
\end{align}
which are matrix-valued functions of $\t$. As shown in \cite{ukhov2012}, $\mE$ and $\mD$ can be efficiently computed using a factorization of $\mA$, which needs to be performed only once for a particular thermal circuit. Taking into consideration all $\steps$ time intervals of $\prof{\mP_\dyn}$, we obtain the following recurrent expression for $k \in \{ 1, \dotsc, \steps \}$:
\begin{equation} \elabel{recurrence}
  \vX_k(\t, \o) = \mE(\t) \vX_k(0, \o) + \mD(\t) \vP_k(0, \o)
\end{equation}
where $\t \in [ 0, \dt_k ]$ and
\begin{align*}
  & \vX_0(0, \o) = \vZero & \vX_k(0, \o) = \vX_{k - 1}(\dt_{k - 1}, \o) \\
  & \vTO_0(0, \o) = \vTO_\amb & \vTO_k(0, \o) = \vTO_{k - 1}(\dt_{k - 1}, \o)
\end{align*}
Here, without loss of generality, we let the initial temperature be equal to the ambient temperature.

In the deterministic case, the analytical solution, which leads to the recurrence given by \eref{recurrence}, can readily be employed to perform the (deterministic) transient temperature analysis (TTA), cf. \cite{ukhov2012}. In the stochastic case, however, where $\vX_k(\t, \o)$, $\vTO_k(\t, \o)$, and $\vP_k(\t, \o)$ are probabilistic quantities, a stright-forward analysis of \eref{recurrence} is difficult to undertake due to the existence of nonlinear correlations between successive steps. In order to tackle this problem, we employ the mathematical framework introduced in \sref{introduction} and further discussed in the following subsection.
