The main idea of our framework is to construct a surrogate model for the joint
power and thermal models of the considered system using PC expansions. Having
constructed this surrogate, such quantities as cumulative distribution functions
(\cdfs) and probability density functions (\pdfs) can be easily estimated.
Moreover, the representations, which we compute, provide analytical formulae for
probabilistic moments, \ie, the expected value and variance are readily
available.

The major stages of our technique are depicted in \fref{algorithm}.

\stage{1}{Parameter Preprocessing (\sref{uncertain-parameters}).}
The PC approach operates on mutually independent random variables. The uncertain
parameters $\vU$ might not satisfy this requirement and, thus, should be
preprocessed; we denote the corresponding independent random variables by $\vZ$.

\stage{2}{Power Modeling (\sref{power-model}).}
The user specifies the power model of the system \via\ a ``black-box''
functional $\oPower$, which computes the total power $\vP(\t, \vU)$ for a
particular temperature $\vTO(\t, \vU)$ and an outcome of the parameters $\vU$.

\stage{3}{Thermal Modeling (\sref{thermal-model}).}
With respect to the thermal specification $\system$ (defined in
\sref{problem-formulation}), a mathematical formulation of the thermal system is
attained. The thermal model closely interacts with the power model from
\stage{2}\ and produces the corresponding temperature profile.

\stage{4}{Surrogate Modeling (\sref{polynomial-chaos}).}
The surrogate model is obtained by traversing the desired time span and
gradually constructing polynomial expansions (in terms of the processed
uncertain parameters $\vZ$ from \stage{1}) of the stochastic power and
temperature profiles. The output is essentially a substitute for the model
produced at \stage{3}\ with respect to the power model determined at \stage{2}.

\stage{5}{Post-processing (\sref{post-processing}).}
The computed PC expansions are analyzed in order to obtain the needed
characteristics of the system, \eg, \cdfs, \pdfs, and moments.

\subsection{Parameter Preprocessing} \slabel{uncertain-parameters}
\input{include/proposed-framework/uncertain-parameters.tex}

\subsection{Power Modeling} \slabel{power-model}
\input{include/proposed-framework/power-model.tex}

\subsection{Thermal Modeling} \slabel{thermal-model}
\input{include/proposed-framework/thermal-model.tex}

\subsection{Surrogate Modeling} \slabel{polynomial-chaos}
\input{include/proposed-framework/polynomial-chaos.tex}

\vspace{-1em}
\subsection{Post-processing} \slabel{post-processing}
\input{include/proposed-framework/post-processing.tex}
