\documentclass[conference]{IEEEtran}

\title{Biography}
\author{}

\begin{document}
  \maketitle

  \section*{Ivan Ukhov}
  {\bf Ivan Ukhov} received the B.Sc. and M.Sc. degrees (both with honors) in computer science and computer engineering from St.~Petersburg State Polytechnical University, St.~Petersburg, Russia, in 2008 and 2010, respectively.

  He is currently a Ph.D. candidate at the Department of Computer and Information Science, Link\"{o}ping University, Link\"{o}ping, Sweden.
  His research is concerned with uncertainty quantification for electronic system design.

  \section*{Petru Eles}
  {\bf Petru Eles} (M'99) received the Ph.D. degree in computer science from the Politehnica University of Bucharest, Bucharest, Romania, in 1993.

  He is currently a Professor with the Department of Computer and Information Science, Link\"{o}ping University, Link\"{o}ping, Sweden.
  His research interests include embedded systems design, hardware-software codesign, real-time systems, system specification and testing, and CAD for digital systems.
  He has published extensively in these areas and coauthored several books.

  Prof. Eles was a corecipient of the Best Paper Awards from the European Design Automation Conference in 1992 and 1994, and from the Design Automation and Test in Europe Conference in 2005, and of the Best Presentation Award from the 2003 IEEE/ACM/IFIP International Conference on Hardware/Software Codesign and System Synthesis.
  He is an Associate Editor of the IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems and of the IEE Proceedings-Computers and Digital Techniques.
  He has served as a Program Committee member for numerous international conferences in the areas of Design Automation, Embedded Systems, and Real-Time Systems, and as a TPC chair and General chair of the IEEE/ACM/IFIP International Conference on Hardware/Software Codesign and System Synthesis.

  \section*{Zebo Peng}
  {\bf Zebo Peng} (M'91--SM'02) received the B.Sc. degree in computer engineering from the South China Institute of Technology, China, in 1982, and the Licentiate of Engineering and Ph.D. degrees in computer science from Link\"{o}ping University, Link\"{o}ping, Sweden, in 1985 and 1987, respectively.

  He is currently a Full Professor of Computer Systems, Director of the Embedded Systems Laboratory, and Chairman of the Division for Software and Systems in the Department of Computer Science, Link\"{o}ping University.
  He served also as the Director of the National Graduate School of Computer Science in Sweden from 2006 to 2008.
  His current research interests include design and test of embedded systems, electronic design automation, SoC testing, fault tolerant design, hardware/software co-design, and real-time systems.
  He has published more than 300 technical papers and four books in these areas.

  Prof. Peng was a recipient of two Best Paper Awards at the European Design Automation Conferences (1992 and 1994), a Best Paper Award at the IEEE Asian Test Symposium (2002), a Best Paper Award at the Design Automation and Test in Europe Conference (2005), and a Best Presentation Award at the IEEE/ACM/IFIP International Conference on Hardware/Software Codesign and System Synthesis (2003).
  He serves currently as Associate Editor of the IEEE Transactions on VLSI Systems, the VLSI Design Journal, and the EURASIP Journal on Embedded Systems.
  He has served on the program committee of a dozen international conferences, including ATS, DATE, DDECS, DFT, ETS, IOLTS, ITC, MEMOCDE, RTCSA, and VLSI-SOC.
  He was the Program Chair of DDECS'04, DATE'08, ETS'07, and ETS'13.
  He served as the Chair of the IEEE European Test Technology Technical Council (ETTTC) in 2006-2009, and has been a Golden Core Member of the IEEE Computer Society since 2005.
\end{document}
