Before diving into details, we show a particular application of the proposed framework. Specifically, we shall perform stochastic PTA of a dual-core platform, wherein the parameters that affect the leakage current are uncertain. The application is a simplified version of the example in \sref{illustrative-example}.

Here, we address one of the most critical parameters influencing on leakage: the effective channel length \cite{chandra2010, juan2011, juan2012, srivastava2010, shen2009}. Due to process variation, the channel length is a \rv, which we denote by $\Leff(\o)$. The variations of $\Leff(\o)$ are split into global (inter-die) $\gLeff(\o)$ and local (intra-die) $\lLeff(\o)$ parts. Assume $\gLeff(\o)$ is shared among the two processors whereas each processor has its own local \rv\ $\lLeff_i(\o)$. Therefore, the channel length of the $i$th processor is
\begin{equation} \elabel{leakage-partition}
  \Leff_i(\o) = \nLeff + \gLeff(\o) + \lLeff_i(\o)
\end{equation}
where $\nLeff$ is the nominal value. Thus, the uncertain parameters, $\vU(\o)$, of the problem have been identified, \ie,
\[
  \vU(\o) = \vec{\lLeff_1(\o), \; \lLeff_2(\o), \; \gLeff(\o) }.
\]
\input{include/assets/application-power.tex}
\input{include/assets/application-temperature.tex}
The variations of $\Leff(\o)$ can be accurately approximated by Gaussian distributions \cite{juan2011, juan2012, srivastava2010}; hence, we assume that $\vU(\o)$ is a Gaussian vector with a given covariance matrix. Since the local \rvs\ are known to have spacial correlations, the uncertain parameters $\vU(\o)$ are not independent. Therefore, at \stage{1}\ of our framework, we transform $\vU(\o)$ into a set of independent \rvs\ denoted by $\vZ(\o) = \vec{\Z_1(\o), \; \Z_2(\o)}$, which is also Gaussian. Note, due to the correlations among $\lLeff_i(\o)$, we were also able to reduce the number of \rvs\ to two making the modeling more efficient. At \stage{2}, we decide on the power model; assume it is given as the following closed-form formula (denoted by $\f$ in \fref{algorithm}):
\begin{align*}
  & \P_i(\t, \o) = \P_{\dyn, i}(\t) + \beta_i \: \exp \left(\vphantom{\T^2_i} \alpha_0 + \alpha_1 \: \Leff_i(\o) \right. \\
  & \qquad {} + \left. \alpha_2 \: \T_i(\t, \o) + \alpha_3 \: \Leff_i(\o) \: \T_i(\t, \o) + \alpha_4 \: \T_i(\o, \t)^2 \right),
\end{align*}
for $i = 1, 2$, where $\P_{\dyn, i}(\t)$ is the dynamic power, and the rest belongs to the leakage power, which is a measurement-based model of the corresponding electrical circuits with the fitting coefficients $\alpha_j$ and $\beta_i$. Assume that the dynamic power profile corresponding to the considered workload, $\profPdyn$, is the one shown in \fref{application-power}. We move on to the thermal model, \stage{3}. The thermal specification $\system$ of the system at hand is assumed to be given (the floorplan of the die, the configuration of the thermal package, \etc). Therefore, we construct an equivalent RC thermal circuit of the system, which is depicted in \fref{circuit} in the appendix. Hence, a mathematical model of heat transfer within the platform is acquired. We transform this model and denote the result by $\mCF(\t)$ and $\mCS(\t)$ in \fref{algorithm}. At \stage{4}, the independent \rvs, power model, and thermal model are fused together under the desired workload to produce the corresponding stochastic power $\profP{\o}$ and temperature $\profT{\o}$ profiles. The obtained stochastic profiles are nothing more than two polynomials of $\Z_1(\o)$ and $\Z_2(\o)$ with time-dependent coefficients. For example, assuming a second-total-order PC expansion, the temperature at the $k$th moment of time is
\begin{align*}
  \vTO_k(\o) &= \pccs_{k1} + \pccs_{k2} \Z_1(\o) + \pccs_{k3} \Z_2(\o) + \pccs_{k4} \Z_1(\o) \Z_2(\o) \\
  & \qquad \qquad {} + \pccs_{k5} (\Z_1(\o)^2 - 1) + \pccs_{k6} (\Z_2(\o)^2 - 1)
\end{align*}
where $\pccs_{ki}$ are vectors with two elements corresponding to the two processors. The expansion for power has the same structure but different coefficients. Such a series might be shorter or longer depending on the accuracy requirements. As we see, our surrogate model has a negligibly small computational cost to undertake UQ at \stage{5}: for any outcome of the uncertain parameters $\vZ(\o) \equiv \vZ$, we can easily compute the corresponding temperature by plugging $\vZ$ into the above equation; the same applies for power. Thus, such characteristics as \cdfs\ and \pdfs\ (see \fref{motivation-pdf}) can be rigorously estimated. Furthermore, the expectation and variance at the $k$th moment of time are calculated as simply as
\[
  \oExp{\vTO_k(\o)} = \pccs_{k1} \hspace{1em} \text{and} \hspace{1em} \oVar{\vTO_k(\o)} = \sum_{i = 2}^{6} \pcn_i \: \pccs_{ki}^2
\]
where $\pcn_i$ are normalization constants, and the squaring should be understood element-wise. For the nominal power profile $\profPdyn$ depicted in \fref{application-power}, we obtain the corresponding stochastic temperature profile $\profT{\o}$ and can observe, \eg, its expectation and standard deviation; they are plotted in \fref{application-temperature}. The displayed curves closely match those obtained via MC simulations with $10^4$ samples; however, our method takes less than a second, on a personal laptop, while MC sampling takes more than a day, which we discuss in \sref{experimental-results}.
